Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
add starsem dir

@@

For each dialogue act corpus, we trained DAR models with BERT encoders pre-trained on the in-domain corpus (\texttt{BERT+ID}) and the combined corpus (\texttt{BERT+CC}).
As before, we experimented with both the fine-tuning and frozen conditions.

>>>>

the in-domain corpus (\texttt{BERT+ID}) and the combined corpus (\texttt{BERT+CC}).

@@

For each dialogue act corpus, we trained DAR models with BERT encoders that received additional pre-training on the three different pre-training corpora. 
As before, we experimented with both the fine-tuning and frozen conditions.
